---
title: "Data analysis"
author: "Bernardo"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

## EDA

```{r message=FALSE, warning=FALSE}
library(readr)
exhibit_10_clean <- read_csv("data/exhibit_10_clean.csv")
```

# Recommendations

## Number of units to order 1

Using the sample data in Exhibit 10, make a recommendation for how many
units of each style Wally Obermeyer should order during the initial
phase of production. Assume that there is no minimum order size
requirement, and that Obermeyer's initial production commitment must be
at least 10,000 units. Assume that an initial order of 10,000 units
leaves sufficient capacity for the second order.

Assuming the demand distribution of each Parka to be a normal
distribution with mean equal to the mean of forecasts, and the standard
deviation being 2 times the individual forecasts standard deviations, we
can use a Monte Carlo method to simulate the expected times the demand
is not exactly met. Using the prices of the Parkas, we can safely

Let the true distribution of demand for each Parka be
$D \sim \mathcal{N}(\mu, \sigma^2)$, we don't know the true value of
$\mu$. We have an estimator
$\hat{D} \sim \mathcal{N}(\hat{\mu}, \hat{\sigma}^2)$ given by the
individual forecasts of several heads of departments. So we say that,
what we want to accomplish is to find, for each Parka, the amount to
order so that the
$$\hat{h_n} = \frac{1}{n}\sum^n_{j=1}h(x_j) \rightarrow \int_xh(x)f(x)dx = E_f[h(X)]$$
Hence, we will create a distribution to approximate the random variable
D. In that way, we can formulate the problem as an optimization problem.
The first step is to map the input, which is our estimated distribution
of demand, to the objective function of profit. We make profit for each
Parka sold, and we sell every Parka we have in stock up to the limit of
the true demand. In addition, we lose profit if we overstock, that is,
order more Parkas then the true demand. Therefore, we model this problem
as:

$$
Profit =   #Selling only the true demand + 
$$

```{r}
# Let the function be for the Gail Parka:
mu <- 2*508.33
dist <- rnorm(10000, mean = mu, sd = 388.1580434)
profit_over <- 8.8
profit_under <- 26.4
price <- 110
f <- function(q, dist, price) 
   mean(pmin(dist,q)*price) - mean(pmax((q-dist),0))*price*.08
q <- optimise(f, c(0,5000), dist = rnorm(10000, mean = 508.33, sd = 388.1580434), price=price, maximum = TRUE)
```

```{r}

set.seed(123)  # for reproducibility

data <- data.frame(exhibit_10_clean)

# Function to optimize
f <- function(q, dist, price) {
  mean(pmin(dist, q) * price * 1.24) - mean(pmax((q - dist), 0)) * price * 0.08
}

# Initialize an empty list to store results
results_list <- list()

# Loop through each row
for (i in 1:nrow(data)) {
  mu_row <- data$mean[i]
  sd_row <- data$std.2[i]
  price_row <- data$Price[i]
  
  # Optimize q for the current row
  q_opt <- optimise(f, c(0,5000), dist = rnorm(10000, mean = mu_row, sd = sd_row), 
                    price=price_row, maximum = TRUE)
  
  # Store the result in the list
  results_list[[i]] <- round(q_opt$maximum/2,0)
}

# Add the results to the dataframe
data$q_optimized <- unlist(results_list)
```

```{r}
# Let the function be for the Gail Parka:
mu <- 2*508.33
dist <- rnorm(10000, mean = mu, sd = 388.1580434)
profit_over <- 8.8
profit_under <- 26.4
price <- 110
f <- function(q, dist, price) 
   mean(pmin(dist,q)*price) - mean(pmax((q-dist),0))*price*.08
q <- optimise(f, c(0,5000), dist = rnorm(10000, mean = 508.33, sd = 388.1580434), price=price, maximum = TRUE)
```

```{r}

set.seed(123)  # for reproducibility

data <- data.frame(exhibit_10_clean)

# Function to optimize
f <- function(q, dist, price) {
  #Selling only the true demand
  sum(dist[dist<q])*price * 1.24
  #Paying for overstocking
  - sum(dist[dist>q])*price*0.08
  #Selling only what we provisioned in the case of understocking
  +sum(dist>q)*q*price * 1.24
}

# Initialize an empty list to store results
results_list <- list()

# Loop through each row
for (i in 1:nrow(data)) {
  mu_row <- data$mean[i]
  sd_row <- data$std.2[i]
  price_row <- data$Price[i]
  
  # Optimize q for the current row
  q_opt <- optimise(f, c(0,5000), dist = rnorm(10000, mean = mu_row, sd = sd_row), 
                    price=price_row, maximum = TRUE)
  
  # Store the result in the list
  results_list[[i]] <- round(q_opt$maximum/2,0)
}

# Add the results to the dataframe
data$q_optimized2 <- unlist(results_list)
```

```{r}
set.seed(123)  # for reproducibility

data <- data.frame(exhibit_10_clean)

# Function to optimize
f <- function(q, dist) {
  #Selling only the true demand
  sum(dist[dist<q]) * price * 0.24
  #Paying for overstocking
  - sum(dist[dist<q]) * price * 0.08
  #Selling only what we provisioned in the case of understocking
  +sum(dist>q) * q * price * 0.24
}

# Initialize an empty list to store results
results_list <- list()

# Loop through each row
for (i in 1:nrow(data)) {
  mu_row <- data$mean[i]
  sd_row <- data$std.2[i]
  
  # Optimize q for the current row
  q_opt <- optimise(f, c(0,5000), dist = rnorm(10000, mean = mu_row, sd = sd_row),
                    maximum = TRUE)
  
  # Store the result in the list
  results_list[[i]] <- round(q_opt$maximum/2,0)
}

# Add the results to the dataframe
data$q_optimized3 <- unlist(results_list)
```

## Number of units to order 2

Using the sample data in Exhibit 10, make a recommendation for how many
units of each style Wally Obermeyer should order during the initial
phase of production. Assume that all ten styles in the sample problem
are made in Hong Kong (a minimum commitment of 600 units per style
ordered), and that Obermeyer's initial production commitment must be at
least 10,000 units. Ignore price differences among styles in your
initial analysis. Clearly spell out the methodology you have used to
make your ordering decisions, and the logic behind your methodology

## What-if 1: All production from China

Repeat your analysis, now assuming that all styles are made in China.
What differences (if any) result?

## Recommended operational changes:

What operational changes would you recommend to Wally to improve
performance? Clearly list the expected benefits from each change. Please
try and be very specific in terms of the changes and benefits in
response to this question

### Change 1: (...)

### Change 2: (...)

## Decision making process on sourcing

How should Obermeyer management think (both short term and long term)
about sourcing in Hong Kong versus China? What sourcing policy would you
recommend?
